---
title: "p8105_hw1_mkr2158"
author: "Matariya Rattanapan"
UNI: "mkr2158"
output: github_document
date: "2025-09-20"
---

# Problem 1

Loading tidyverse and moderndive package

```{r}
library(tidyverse)
library(moderndive)
```

Retreiving the dataset
```{r}
data("early_january_weather")
```

The variables in this dataset include the origin, time of recording (year, month, day, and hour), temperature, dewpoint, relative humidity, wind direction, speed, gust, precipitation, pressure, visibility, and data and hour of recording.

Some important variables to consider are:
temp = temperature in Fahrenheit
time_hour = date and hour of the recording
humid = relative humidity

The dataset `early_january_weather` contains `r nrow(early_january_weather)` hourly measurements and `r ncol(early_january_weather)` variables.

The mean temperature from the dataset `early_january_weather` is `r mean(pull(early_january_weather,temp))`.

```{r}
ggplot(early_january_weather, aes(x=time_hour, y=temp, color=humid)) + geom_point()
ggsave("early_january_weather_scatter.pdf", height = 4, width = 6)
```

This scatter plot shows that as the days in January went by, the temperature would generally increase. In early January, the temperatures were as low as around 25 degrees Fahrenheit, and towards the end it went up to nearly 60 degrees Fahrenheit. Lower humidity was also seen in earlier January days during low temperatures. Contrastingly, higher humidity was seen towards the end of January alongside higher temperatures. 

# Problem 2

Making a data frame

```{r}
hw1_df = 
  tibble(
    vec_numeric = rnorm(10),
    vec_char = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"),
    vec_logical = vec_numeric > 0,
    vec_factor = factor(c("Screened", "Refused", "Consented", "Screened", "Refused", "Consented", "Screened", "Refused", "Consented", "Screened"))
  )
```


