---
title: "p8105_hw1_mkr2158"
author: "Matariya Rattanapan"
UNI: "mkr2158"
output: github_document
date: "2025-09-20"
---

# Problem 1

Loading tidyverse and moderndive package

```{r}
library(tidyverse)
library(moderndive)
```

Retreiving the dataset
```{r}
data("early_january_weather")
```

The variables in this dataset include the origin, time of recording (year, month, day, and hour), temperature, dewpoint, relative humidity, wind direction, speed, gust, precipitation, pressure, visibility, and data and hour of recording.

Some important variables to consider are:
temp = temperature in Fahrenheit
time_hour = date and hour of the recording
humid = relative humidity

The dataset `early_january_weather` contains `r nrow(early_january_weather)` hourly measurements and `r ncol(early_january_weather)` variables.

The mean temperature from the dataset `early_january_weather` is `r mean(pull(early_january_weather,temp))`.

```{r}
ggplot(early_january_weather, aes(x=time_hour, y=temp, color=humid)) + geom_point()
ggsave("early_january_weather_scatter.pdf", height = 4, width = 6)
```





